NFC and burnout in teachers - A replication and extension study

### 2022-07-21 Manuscript/Revision_Letter.Rmd
replied to more from rev3

\Assignment{JZ}
\Done

@@

\Assignment{AS}
\Done

@@

\Assignment{JZ}
# Comment: see Table 2 in Fleischhauer et al. (2019)

@@

>>>>

@@

@@

We have added the correlations of NFC with neuroticism, self-esteem, and locus of control in the manuscript:

> NFC on the other hand shows opposite associations with those variables (r = -.19 with passive coping (Grass et al., 2018), r = -.19–-.33 with neuroticism (Fleischhauer et al., 2019), r = .42 with self-esteem (Osberg, 1987), r = .32 with internal locus of control (Fletcher et al. 1986)), suggesting that people high in NFC are less prone to experience burnout.

In the study done by Fleischhauer et al. (2019, https://doi.org/10.3389/fpsyg.2019.00420, Table 2), NFC could provide incremental validity in predicting the MBI score and its subscales over and above the Five Factor model.
The adults in this study were a population-based sample of over 4,100 participants from different work backgrounds.

Thank you for suggesting to provide more information on the characteristics of the Grass et al. sample.
We have added the following information to the manuscript:

> Grass et al. (2018) investigated such a mediation in a sample of 167 students, who were studying to become teachers in primary, secondary, special needs, or vocational schools, and who had been studying for M ± SD = 5.13 ± 2.63 semesters.

We wanted to replicate the findings of Grass et al. (2018) in a sample of teachers to investigate the different mechanisms that influence the development of burnout in different life/career stages within the same profession.
As burnout mostly affects social jobs and theories of person-environment fit have been discussed for quite some time, it begs the question whether the structure of social jobs causes burnout or whether the type of employee in social jobs is more prone to burnout.
Studying the same profession in different stages can shed light on this issue.

@@

We did not have specific hypotheses about the relations of the demand-resource-ratios to each other.
Initially it would stand to reason that they are not substantially correlated at all, since each participant might have a unique level of demands and resources, so they should score high in one of the variables and rather low in the other two.
However, as they correlation table (Table 2) shows, this is not the case.
DTH and DTL are positively correlated, and both are negatively correlated with DRF.
Although initially counterintuitive, these associations are quite likely in practise: A teacher can have a very high workload in a strict time frame (high DTH) but the work itself might not be interesting or cognitively stimulating at all (high DTL), such as teaching the same material year after year, not being able to influence the syllabus, teaching at a much lower standard than what the teacher learned at university, keeping notorious troublemakers under control, having parent-teacher conferences until the late evening, etc.
So a surplus of demands and a surplus of resources can co-exist, but not together with a demand-resource-fit.
We have added the following section to the discussion:
